\documentclass[phd,bottom,nosig]{usbthesis}
%\includeonly{chapter1}
\bibliographystyle{apj}
\usepackage{graphicx}
\usepackage{deluxetable}
\usepackage{longtable}
\usepackage{color}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{array}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{afterpage}
\usepackage{dirtytalk}
\usepackage{hhline}
\usepackage{url}
\usepackage{verbatim}
\usepackage{pdfpages}
\usepackage{hyperref} % see the file hyperref.cfg for options
\usepackage[T1]{fontenc}
%\usepackage{indentfirst} % I find it ugly if the first paragraph is indented
\usepackage{footmisc} % provides \footref and \mpfootnotemark commands
\usepackage{xspace}
\usepackage{natbib}
%\usepackage[nottoc]{tocbibind}
%Make caption labels bold
\usepackage[labelfont=bf]{caption}

%Edit graphics path?



%\sloppy

% Math definitions
%\input{mathdefs}

% Latin abbreviations
\providecommand*{\eg}{\emph{e.\,g.}\xspace}%
\providecommand*{\ie}{\emph{i.\,e.}\xspace}%

%CREF CITATION COMMAND
\newcommand{\crefrangeconjunction}{--}
\newcommand{\micron}{$\mathrm{\mu m}$}
\newcommand{\file}{}
\newcommand{\aj}{AJ}			% Astronomical Journal
\newcommand{\araa}{ARA\&A}		% Annual Review of Astron and Astrophys
\newcommand{\apj}{ApJ}			% Astrophysical Journal
\newcommand{\apjl}{ApJL}		% Astrophysical Journal, Letters
\newcommand{\apjlett}{ApJL}		% Astrophysical Journal, Letters
\newcommand{\apjs}{ApJS}		% Astrophysical Journal, Supplement
\newcommand{\apjsupp}{ApJS}		% Astrophysical Journal, Supplement
\newcommand{\ao}{Appl.~Opt.}		% Applied Optics
\newcommand{\apss}{Ap\&SS}		% Astrophysics and Space Science
\newcommand{\aap}{A\&A}			% Astronomy and Astrophysics
\newcommand{\astap}{A\&A}		% Astronomy and Astrophysics
\newcommand{\aapr}{A\&A~Rev.}		% Astronomy and Astrophysics Reviews
\newcommand{\aaps}{A\&AS}		% Astronomy and Astrophysics, Supplement
\newcommand{\azh}{AZh}			% Astronomicheskii Zhurnal
\newcommand{\baas}{BAAS}		% Bulletin of the AAS
\newcommand{\jrasc}{JRASC}		% Journal of the RAS of Canada
\newcommand{\memras}{MmRAS}		% Memoirs of the RAS
\newcommand{\mnras}{MNRAS}		% Monthly Notices of the RAS
\newcommand{\pra}{Phys.~Rev.~A}		% Physical Review A: General Physics
\newcommand{\prb}{Phys.~Rev.~B}		% Physical Review B: Solid State
\newcommand{\prc}{Phys.~Rev.~C}		% Physical Review C
\newcommand{\prd}{Phys.~Rev.~D}		% Physical Review D
\newcommand{\pre}{Phys.~Rev.~E}		% Physical Review E
\newcommand{\prl}{Phys.~Rev.~Lett.}	% Physical Review Letters
\newcommand{\pasp}{PASP}		% Publications of the ASP
\newcommand{\pasj}{PASJ}		% Publications of the ASJ
\newcommand{\pasa}{PASA}   % Publications of the Astronomical Society of Australia
\newcommand{\qjras}{QJRAS}		% Quarterly Journal of the RAS
\newcommand{\revmodphys}{Rev.\ Mod.\ Phys.} %Rev Mod Phys
\newcommand{\skytel}{S\&T}		% Sky and Telescope
\newcommand{\solphys}{Sol.~Phys.}	% Solar Physics
\newcommand{\sovast}{Soviet~Ast.}	% Soviet Astronomy
\newcommand{\ssr}{Space~Sci.~Rev.}	% Space Science Reviews
\newcommand{\zap}{ZAp}			% Zeitschrift fuer Astrophysik
\newcommand{\nat}{Nature}		% Nature
\newcommand{\iaucirc}{IAU~Circ.}       	% IAU Circulars
\newcommand{\aplett}{Astrophys.~Lett.} 	% Astrophysics Letters
\newcommand{\apspr}{Astrophys.~Space~Phys.~Res.}% Astrophysics Space tPhysics Research
\newcommand{\fcp}{Fund.~Cosmic~Phys.}  % Fundamental Cosmic Physics
\newcommand{\gca}{Geochim.~Cosmochim.~Acta}   % Geochimica Cosmochimica Acta
\newcommand{\grl}{Geophys.~Res.~Lett.} % Geophysics Research Letters
\newcommand{\jcp}{J.~Chem.~Phys.}	% Journal of Chemical Physics
\newcommand{\jgr}{J.~Geophys.~Res.}	% Journal of Geophysics Research
\newcommand{\nphysa}{Nucl.~Phys.~A}   % Nuclear Physics A
\newcommand{\physrep}{Phys.~Rep.}   % Physics Reports
\newcommand{\physscr}{Phys.~Scr}   % Physica Scripta
\newcommand{\planss}{Planet.~Space~Sci.}   % Planetary Space Science
\newcommand{\procspie}{Proc.~SPIE}   % Proceedings of the SPIE
\newcommand{\ES}{$\Sigma_{\overline{E}}$}

%\hyphenation{put words here which LaTeX does not hy-phen-ate
%pro-per-ly}

\newcommand{\WS}{\textit{WISE}}
\newcommand{\WSAC}{\textit{WISE} All-Sky}

\def\hip{\textit{Hipparcos}}
\def\akari{\textit{AKARI}}
\def\iras{\textit{IRAS}}
\def\iso{\textit{ISO}}
\def\spitzer{\textit{Spitzer}}
\def\mass{\textit{2MASS}}
\def\p14{PMH14}
\newcommand{\arcsec}{$''$}
\newcommand{\arcmin}{$'$}

\author{Rahul Indrakant Patel}%
\title{The Census of  Warm Debris Disks in the Solar Neighborhood from \WS\ and \hip}%

\month{September} \year{2015}%

\program{Physics}%

\begin{document}

\singlespacing %
\pagenumbering{roman} %

\maketitle %
%\makeapproval %


\newpage
\pagenumbering{gobble}

\vspace*{32\baselineskip}
\vspace*{1\baselineskip}
\centerline{Copyright by}
\centerline{Rahul Indrakant Patel}
\centerline{2015}


\newpage
\pagenumbering{roman}
\setcounter{page}{2}

%Add committee page
\centerline{\bf{Stony Brook University}}
\vspace*{1\baselineskip}
\centerline{The Graduate School}
\vspace*{2\baselineskip}
\centerline{Rahul Indrakant Patel}
\vspace*{2\baselineskip}
\centerline{We, the dissertation committee for the above candidate for the}
\vspace*{1\baselineskip}
\centerline{Doctor of Philosophy degree, hereby recommend}
\vspace*{1\baselineskip}
\centerline{acceptance of this dissertation}
\vspace*{2\baselineskip}
\centerline{\bf{Stanimir Metchev - Dissertation Advisor}}
\centerline{\bf{Professor, Department of Physics and Astronomy}}
\vspace*{1\baselineskip}
\centerline{\bf{Michael Zingale - Chairperson of Defense}}
\centerline{\bf{Professor, Department of Physics and Astronomy}}
\vspace*{1\baselineskip}
\centerline{\bf{Matthew Dawber - Committee Member}}
\centerline{\bf{Professor, Department of Physics and Astronomy}}
\vspace*{1\baselineskip}
\centerline{\bf{Rebecca Oppenheimer - Committee Member}}
\centerline{\bf{Professor, American Museum of Natural History}}
\vspace*{2\baselineskip}
\centerline{This dissertation is \textbf{??accepted??} by the Graduate School}
\vspace*{3\baselineskip}
\centerline{Charles Taber}
\centerline{Dean of the Graduate School}

\newpage

\begin{abstract}
    Debris disks are optically thin circumstellar disks around main-sequence stars, comprised of micron-sized grains. The dust is generated from destructive collisions of planetesimals, induced from gravitational perturbations by large planets. Debris disks act as signposts for planetary systems, and are useful in understanding architectural similarities to the Solar System's disk.  The dust in these disks can be detected by their thermal infrared flux, measured as an excess above the photospheric emission. Dust at different circumstellar locations, inferred from the peak wavelength of the detected emission, can act as a probe for local dynamical activity in the system. Over the last thirty years, cold disks, analogous to the Kuiper Belt, have constituted the bulk of debris disk detections. Warm disks, analogous to the Main Asteroid belt, can act as signposts for dynamical activity in the terrestrial planet zone, but are rare in contrast. %Thus, without proper contextual characterization of the inner warm dust regions, we are left with an incomplete picture of planetary system evolution.
The Wide-Field Infrared Survey Explorer (\WS) space telescope mapped the entire sky in two near-IR and two mid-IR bands in 2012. The two mid-IR bands are well placed to probe dust emission in the TPZ of these stars, at sensitivities greater than the last all-sky IR survey (\iras) in 1983. \WS\ also provides us for the first time an opportunity to contemporaneously measure the photospheric and IR excess wavelengths of the entire sky, increasing sensitivity to fainter levels of dust.  
	
	In this thesis, I present an unbiased survey of warm disks around main-sequence Hipparcos stars in the solar neighborhood, detected using data from the \WS\ All-Sky Database. Our series of surveys builds upon each other to find previously undetected faint, warm debris disks by including bright photometrically saturated stars in \WS, using empirical photospheric colors, removing several non-trivial false-positive sources, and verifying and validating these detected excesses.  This thesis adds a substantial number of clean, new disk targets to the census of debris disks in the solar neighborhood that will enhance our understanding of the formation and evolution of planetary systems.

\end{abstract}

\begin{dedication}
   Probably to a lot of people. \textbf{I was writing this part of my thesis when New Horizon's crossed Pluto earlier in the day.}
\end{dedication}

\tableofcontents %
\listoffigures %
\listoftables %

\begin{acknowledgements}

\end{acknowledgements}

\pagestyle{thesis}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newpage
\pagenumbering{arabic}

\chapter{Introduction} \label{chap:intro}
\input{Ch1/Ch1.tex}

\chapter{Detecting Debris Disks with the Wide-Field Infrared Survey Explorer}\label{chap:wise_method}
\input{Ch2/Ch2.tex}

\chapter{Identification of Warm Debris Disks Within 75~pc} \label{chap:iddisks}
\input{Ch3/Ch3.tex}
\clearpage
%\setboolean{@twoside}{false}
%\includepdf[pages=-,offset=75 -75]{Ch3/WISEPaper_PMH14.pdf}


\chapter{Improved Methods To Verify \WS\ Debris Disks With Weighted Colors and unWISE Images}\label{chap:confirm}
\input{Ch4/Ch4.tex}

\chapter{Identification of Warm Debris Disks In The Galactic Plane And Out to 120~pc}\label{chap:120pc}
\input{Ch5/Ch5.tex}

\chapter{Summary of Results}\label{chap:summary}
\input{Ch6/Ch6.tex}


\chapter{Discussion}\label{chap:discussion}
\input{Ch7/Ch7.tex}


\chapter{Future Direction}\label{chap:future}

\bibliography{References_PhD}


\appendix
\input{Appendix/appendix.tex}

%\include{appendix1}
%\include{appendix2}
% ...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}